In-situ visualization of regional-scale natural hazards with Galaxy and Material Point Method

### 2022-02-08 response-reviewers.tex

\shortpoint{This paper doesn't fit the style of the examples that were provided by the editors. Its formatted as a technical paper, although I found that the content wasn't overly technical in most places. Details such as "we generally leave this as localhost/1900 and use an SSH tunnel to connect that local port to wherever the Galaxy root process is running" is probably too much that doesn't add much to the understanding of the contribution.}
\shortreply{We agree with the reviewer and the statement has been removed.}

\shortpoint{Improve the introduction.}
\shortreply{Thank you for the comment. We have revised the introduction to make it clear.}

\reviewersection

\begin{point}
The topic of this manuscript is of a great importance to all readers who are interested in exascale simulations and visualization in the STEM field. The I/O operations during the simulation is always a burden for HPC applications, to avoid such problem, in-situ visualization is needed and should be without extra time cost. The authors coupled the MPM with Galaxy to carry out the in-situ visualization for the Oso landslide with a negligible time cost. The manuscript discussed how exascale simulations needs rendering engines capable of rendering billions of light paths. Most rendering engines only sample a limited number of random light paths at each time step producing images with low visual quality. Therefore, this study used TACC Galaxy Ray tracing engine which offers distributed asynchronous in-situ visualization capabilities for exascale simulations. 
\end{point}
\shortreply{Thank you for your encouraging comments.}
\printbibliography
\end{document}
